Formalizing Stack Safety as a Security Property

### 2021-07-08 submission3/main.tex
Gloss and reformat criteria

For criterion (1), we contend that our property definitions are at least as
intuitive as theirs, while being phrased in interestingly different terms.
We use the language of formal security
properties to apply well-established concepts and formal techniques
of non-interference, and we define our properties in terms of
traces of memory and register states, rather than in terms of an
ad-hoc abstract machine.
Which approach is ``better'' is probably a matter of taste, but ours
has at least the merit of explicitly relating stack safety to existing
notions of security.

With respect to criterion (4), we believe that our support
for dynamically changing notion of adversaries, as outlined in point (i) above,
captures a better definition of safety than LSE; moreover, our observational
properties capture an even richer and more intensional notion of stack safety
that can be applied to a broader range of enforcement mechanisms and code features.

As for criterion (5), we have demonstrated that our approach extends to
coroutines, a first step towards multithreading.  Dynamic code generation is
more challenging, but StkTokens does not yet handle this either.  StkTokens
is specifically set up to address criterion (3), while this is not a goal of
our work. We agree that criterion (2), usefulness of the safety criterion
for carrying out formal proofs (about individual programs), is important;
demonstrating it for our proposal remains future work.  Instead, we have
chosen to focus on property-based random testing as a methodology for
validating enforcement mechanisms.

>>>>

For criterion (1), intuitiveness, we contend that our property definitions are at least as
intuitive as theirs, while being phrased in interestingly different terms.
We use the language of formal security
properties to apply well-established concepts and formal techniques
of non-interference, and we define our properties in terms of
traces of memory and register states, rather than in terms of an
ad-hoc abstract machine.
Which approach is ``better'' is probably a matter of taste, but ours
has at least the merit of explicitly relating stack safety to existing
notions of security.

With respect to criterion (4), capturing programmers' informal
understanding of stack safety, we believe that our support
for dynamically changing notion of adversaries, as outlined in point (i) above,
captures a better definition of safety than LSE; moreover, our observational
properties capture an even richer and more intensional notion of stack safety
that can be applied to a broader range of enforcement mechanisms and code features.

As for criterion (5), broad applicability, we have demonstrated that our approach extends to
coroutines, a first step towards multithreading.  Dynamic code generation is
more challenging, but StkTokens does not yet handle this either.

StkTokens
is specifically set up to address criterion (3), reusability in secure
compilation chains, while this is not a goal of
our work.

We agree that criterion (2), usefulness of the safety criterion
for carrying out formal proofs (about individual programs), is important;
demonstrating it for our proposal remains future work.  Instead, we have
chosen to focus on property-based random testing as a methodology for
validating enforcement mechanisms.
